DRAFT: v6.dev \\ Vibration Characterisation of Strollers and\\ Cargo Bicycles for Transporting Infants\\ \vspace{2mm} \large{Including Recommendations for Users, Designers, Manufacturers, and Researchers} \\

### 2025-08-28 main.tex
Update tex file from overleaf.

\color{black}
\begin{abstract}
  Infants are transported in strollers and in baby seats mounted on cargo
  bicycles. The infants experience whole-body vibration during the associated
  walking and cycling trips, but there is little existing knowledge about
  associated comfort and health effects. To improve this, we measure the seat
  pan acceleration of five strollers and two styles of cargo bicycles with dummy
  infants representing ages 0 to 9 months over six different road surfaces of
  varying road roughness at typical travel speeds. The five strollers included
  three modern systems and two vintage systems with some level of suspension.
  One cargo bicycle had electric support enabling speeds up to 25~\si{\kph}. We
  report average seat pan acceleration for 78 different scenarios and
  investigate the effects of road surface, vehicle, seat type, and travel speed.
  Using the whole-body vibration ISO standards, we show that rough road
  surfaces, amplified by travel speed, may have health risks for travel
  durations as low as \SIrange{10}{30}{\min}. Stroller designs from 50 years ago
  significantly reduce vibrations, relative to most modern strollers we tested,
  indicating the need for a return of suspension elements. Cargo bicycles ridden
  at the maximum electric bicycle speed over paver bricks can cause
  accelerations that should likely be avoided except for only the shortest of
  durations until more direct evidence of risks to infants is studied. Standards
  are needed for infant transport testing and evaluation, designers need to
  incorporate better suspension for infants, and research is needed to develop
  clear and direct connections to health and comfort effects.
\end{abstract}

@@

\section{Introduction}
%Paragraph to introduce baby transport
When a baby is born, it is not able to walk. To move around or travel, it must
be either carried by adults or transported in a suitable means of wheeled
transport. Until about a century ago,  babies mainly stayed at home. This still
is customary in some non-Western cultures. A century ago, perambulators were
used to transport infants outdoors. However, mothers were advised that a playpen
in the garden is healthier than the use of a perambulator, partly because the
vibrations generated by a perambulator were deemed not comfortable and even
harmful for the baby~\cite{behrend1931}, even though in those days perambulators
had ample suspension. Since about 1970, cars became ubiquitous and the heavy and
sizeable perambulators became strollers: lighter and smaller products to enable
easy transportation in a car. Over the years, new means of transportation came
into use for infants: cars with a child car seat, bicycles with a bicycle seat
and cargo bicycles with either a car seat or a baby shell.

%Paragraph to introduce baby vibration in transportation
All means of transport cause vibration, which is transferred to the infant
sitting or lying in it. Unlike the advice in the 1930s, vibration is seemingly
not a subject of attention in the present design of these products. On the
contrary, modern strollers do not have much suspension and cargo bicycles which
generate more vibration are increasingly used for infants. Interestingly, in the
literature we could find little about the maximal vibration load that babies and
older children can receive during transport without discomfort or harm, and
vibrations generated by infant transport are also only sparsely investigated.
Therefore the effect of transport on infant comfort and health can not easily be
assessed. To establish the amount of vibration that infants are subjected to in
transportation products, we investigated the vibration that infants receive
during transport in strollers and cargo bicycles.

% Paragraph about motivation
Cycling, one of the active transportation modes, is advantageous for
health~\cite{Oja1998} and greatly contributes to reducing CO\(_2\) emissions, congestion, and air pollution~\cite{Neves2019}. As a result, bicycles are
increasingly used as a means to deliver goods to consumers, and also for daily
commuting to work and personal matters (shopping, commuting with
children/infants, and others). Among all journeys in the EU, 20-40\% are by
bicycle or on foot, with bicycle trips most frequent in the Netherlands,
Denmark, and Sweden and less frequent in Finland. Various countries and
employers provide incentives to increase the use of bicycles. However, some
challenges need to be overcome to secure the wide acceptance and use of active
transportation modes. One of these challenges is the comfort levels experienced
by riders and passengers (i.e., infants/children in cargo bicycles), which is a
multifaceted aspect~\cite{ayachi2015identifying} and critical for the wide
acceptance and use of bicycles as a daily means of transport. Meanwhile, this is
a topic that is of great interest and requires attention when it comes to
infants' transportation with strollers or bicycles.

% Paragraph about comfort in bicycles
The research on cyclist comfort is a natural starting point for investigations
of similar road-induced vibrations for infants.
Comfort on bicycles~\cite{too1990biomechanics} is mainly affected by physical
comfort and the impact of environmental factors (weather, geometry of the route,
and road roughness).  
Physical comfort is related to mechanical (bicycle and component design),
biomechanical (whole-body vibrations, human body dynamics, and kinematics) and
physiological factors (individual characteristics, e.g. sex, body size, weight
and others).
While there is extensive literature exploring the impact of environmental
factors (i.e., irregular road surface quality, weather conditions) on cyclists'
comfort~\cite{Stinson2003,Hagemeister2003,ayachi2015identifying,Verhoeven2017,Teixeira2020},
there is limited work on understanding the biomechanical and physiological
factors of comfort while being carried by bicycle (infants/children in bicycle
seats, on cargo bicycles, or in trailers). A particular concern is the transport
of infants under one year, who cannot well express any experience of discomfort
or pain.
Similar concerns are raised when it comes to strollers, where infants are also
exposed to vibrations induced by roads. 
In this paper, we will explore biomechanical comfort by assessing the whole-body
vibrations that could be experienced by transported infants both in cargo
bicycles and strollers, and evaluating potential health risks and discomfort
that might arise.

% Paragraph about transmission of vibrations
Biomechanical comfort is mostly related to the vibrations induced by road
irregularities and transmitted via the vehicle to the human body and head while
being driven~\cite{too1990biomechanics}. 
According to the literature, road irregularities are a critical factor for the
amplitude of the resulting vibrations experienced by the bicyclists and
passengers, as the vibrations induced on the body and head are not efficiently
isolated due to the lack of or inadequate suspension systems in most of the
bicycle models~\cite{vasudevan2017comparison} or strollers.
The bicycle or stroller design and its specific configuration can affect the
sitting posture, and eventually the transmissibility of the
vibrations~\cite{Brand2020,Verma2016}.
The sitting posture can also vary in case of children/infants who may be
transported sitting or lying down in a different posture and location than the
cyclist (e.g. above a wheel when in a bicycle seat) and in/on a different `seat'
(a car seat, bicycle seat, stroller seat, or cot). 
These all influence the level of whole-body vibrations and the transmission of
the vibrations from the seat to the body and head.
Furthermore, the amplitude of the vibrations experienced by
bicyclists/passengers/transported infants while biking or being transported in a
stroller may increase because of increased travelling speed either due to
running with a stroller or due to the increased power offered by electric
bicycles (with and without trailers).
For the latter, the average speed of electric bicycles and speed pedelecs is
19\% higher (21.0~\si{\kph} and up to 63\% higher (28.1~\si{\kph}),
respectively, than the average speed of conventional bicycling~\cite{SWOV2022}.
The intensity of these vibrations could become even more critical with the
change of load, which could be related with age and size of the infant/children
transported. However, there is limited literature exploring the whole-body
vibrations of infants and children being transported by bicycles with trailers,
cargo bicycles, stroller seats and others
~\cite{Ota2012,Ota2014,Kanya-Forstner2020, vanDriessche2018,
Schwanitz2020,MalteChildComfort2022}.
At the same time, the available literature is mostly focusing on comfort rather
than health risks.

% Paragraph about children in bicycles
One of the research fields closely related to vibrations acting on infants
during transportation is that of inflicted head injury by shaking trauma
(IHI-ST). However, there is a lack of reliable, applicable, validated injury
thresholds for assessing IHI-ST risks~\cite{hutchinson2024modeling}. Similarly,
even if there are significant indications that the vibration amplitude affects
comfort in bicycles or strollers, there are no standard assessment methods or
guidelines available with regards to their design. ISO~2631~\cite{ISO2631}, the
international standard for assessing whole-body vibrations, was derived using
datasets on motion platforms, adults as human participants and sitting postures
which are adopted in passenger vehicles rather than on bicycles.
This inconsistency was captured by Gao~et~al.~\cite{Gao2018}, who derived
different limits of comfort for adults riding on bicycles based on their
subjective feedback, compared to the vibration limits suggested by
ISO~2631-1.
In addition, the exposure time to the vibrations is not considered as a factor
of comfort by the ISO~2631-1, despite having a clear impact on health risks
according to the European Directive (2002/44/EC, 2002)
\cite{directive2002directive}.

% Paragraph Potential effects of vibrations on adults
Despite the lack of clarity with regards to comfort assessment or inflicted head
injury by shaking trauma for children/infants on bicycles, there are clear
indications in the literature that these should be explored and considered.
About 36\% of males and 42\% of females in a total sample of 900 people had
various complaints about comfort~\cite{groenendijk1992sitting}.
Discomfort for both men and women occurred even during short bicycle trips
(\SIrange{3}{10}{\kilo\meter}). However, results from research into comfort of
adult cyclists can not be applied directly to infants or children sitting or
lying in transportation systems.

Schwanitz~et~al.~\cite{Schwanitz2020} assessed accelerations in a child bicycle
trailer riding over smooth asphalt, gravel, and cobblestones using ISO~2631-1
weighted RMS vertical accelerations.
Anthropomorphic children shaped sandbag dummies (baby and toddler sizes) were
used as lumped masses to represent the child body. According to the results, tyre pressure and the number of
passengers had no significant effect on vibration magnitude, but road surface
and travel speed did. 
The baby sized dummy (5~\si{\kilo\gram}) experienced 20\% higher vibration than
the toddler sized dummy (10~\si{\kilo\gram}), while the measured values
generally exceeded the ISO~2631-1 vibrational comfort of adults.
Rothhämel~et~al.~\cite{MalteChildComfort2022} conducted measurements using a
trailer seat and a tadpole configuration three-wheel cargo bicycle on smooth
asphalt and cobblestones for speeds between \SIrange{10}{20}{\kph}. 
After weighting the accelerations using ISO~2631-1 methods, they found a large
increase of the vibration amplitude on cobblestones compared to asphalt on the
same speed range. The child trailer exhibited larger weighted RMS accelerations
than the cargo bicycle with the child seat between the front wheels. 
Both the trailer and cargo bicycle child seats had generally larger magnitude
vibrations than experienced in an automobile seat travelling at 30~\si{\kph} on
a rough road \cite{gromadowski2013analysis}. Rothhämel and
Liu~\cite{rothhamel2023comfort} conducted measurements with a
6.5~\si{\kilo\gram} mass representing an infant with various tyre pressures. All
their values fell into the ``extremely uncomfortable'' zone for the ISO~2631-1.

In addition to the studies with dummies or lumped masses representing
infants, Kanya-Forstner~\cite{Kanya-Forstner2020} measured acceleration in
bicycle child trailers with human subjects aged 12 months to 6 years over
asphalt and gravel terrain (averaged speed of 12~\si{\kph} over the
20~\si{\minute} ride). 
According to the health assessment using ISO~2631-1, the vibrations are similar
to the ones experienced in car seats in vehicles and illustrated moderate or low
health risk for a 2~\si{\hour} duration.
On the other hand, if not corrected for duration, the values point to moderate
and high risks. The terrain type had the greatest influence on vibration
exposure levels followed by trailer type, while gel cushions as support did not
significantly influence vibration measured at the seat/pan interface. Hence,
there is a need to re-focus on the impact of vibrations on infants and
children's health and comfort~\cite{rybarczyk2020physiological} to ensure the
safe, comfortable and wide use of bicycles.

% Don't edit, working to change the following paragraph
In the context of infants transportation with stroller seats, Kok
Siong~\cite{lim2018study} carried out an indoor and an outdoor experiment to
capture the vibrations transmitted onto the seat and backrest of a baby
stroller, using weights from \SIrange{4}{14.14}{\kilo\gram}, and  a child
subject of 10.30~\si{\kilo\gram} as well as a dummy weighing
10.30~\si{\kilo\gram}. 
The comfort levels for the indoor testing were labelled as `Fairly
uncomfortable' to `A little uncomfortable', but the outdoor testing resulted in
`Extremely uncomfortable' and `Fairly uncomfortable' values. They used both a
child and dummy for the experiments, identifying similar patterns. However, the
results still consider ISO~2631-1 standard, which is designed for adults and
specific postures. In a similar research, Sierzputowski~
et~al.~\cite{sierzputowski2021pilot} investigated vibrations induced in a modern
and
an older stroller, when moving on different surfaces: asphalt road, concrete
paving blocks, concrete plates, dirt road, lawn and damaged concrete. The
obtained weighted RMS acceleration values based on ISO~2631-1 were several times
in the range of the highest discomfort ($>$2~\si{\mps\squared}). 
Another research which also included children as test subjects was conducted by
Okajima~et~al.~\cite{okajima2020dynamic} measuring vibrations that seven
children received, sitting upright in a stroller, when riding over a protrusion
(13x60 mm) with either one wheel or two wheels. 
The children were 3 to 6 years old, boys and girls, weighing
\SIrange{15.94}{19.96}{\kilo\gram} and measuring
\SIrange{98.0}{112.4}{\centi\meter} in length. 
Based on the results, the infant’s head and chest exhibit strong vibrations at
1~\si{\hertz} along all three axes (x,y and z), vibrate easily along the
y-direction at 2~\si{\hertz}, and are less likely to vibrate at more than
8~\si{\hertz}. 
This result is critical as this range of frequencies is very common in bicycles
and strollers. However, they did not assess the comfort and the health risk when
the children were exposed to these vibrations. 
Despite significant research on the effect of whole-body vibrations on
children's comfort, there is limited research on infants.

This paper reports on the vibration induced on infants of different ages when
transported in strollers and cargo bicycles. 
Vibration can be related to discomfort and might lead to negative health
consequences. However, the topic is poorly addressed in scientific literature,
and only a few studies focus on the effect of vibration on babies as reviewed
above. 
To measure the actual vibration transmitted to infants, we equipped five
strollers and two cargo bicycles with inertial measurement units (IMU) and
conducted 78 experiments on different road surfaces and travel speeds, using
dummies representing the size and mass of 0, 3, and 9 months old infants.
We present results in the time and frequency domains, which allows comparing
vertical accelerations at the baby-seat interface, as recommended by ISO~2631-1
standards for vibration discomfort.
We investigated the influence of different variables on vibration, such as type
of vehicle, baby seat, travelling speed, dummy size and mass, and road surfaces
and provide recommendations to users, designers, and future researchers based on
the findings.

\section{Methods}
%
\subsection{Test Equipment}
%
Vibration measurements were conducted at approximate constant speed using five
different strollers, two cargo bicycles, and two baby
seats~\footnote{Appendix~\ref{app:equipment} provides figures and technical
descriptions of all the strollers and cargo bicycles.}, chosen for their
popularity and/or distinctive features:

\begin{description}
\item[Strollers] A selection of vintage and modern strollers for carrying
infants. The modern strollers are configurable as cots for newborns and as seats
for older infants.
%
\begin{description}
  \item[Maxi-Cosi Street Plus] This stroller comes with a cot configuration (0-3
  months) and an infant seat option. It has large wheels, with only a marginal
  suspension system.
  (\href{https://www.maxi-cosi.nl/kinderwagens/street-plus?color_swatch_id=5519}{Maxi-cosi website})
  \item[Stokke BABYZEN YOYO 0+] The smallest foldable stroller on the market. It
  has only a marginal suspension system and smaller wheels compared to those of
  other strollers available on the market.
  (\href{https://tinylibrary.nl/products/kinderwagen-babyzen-yoyo-0-plus}{Model
  rented for the experiment})
  \item[Bugaboo Fox 5] Featuring large wheels and a suspension system that makes
  it an all-terrain stroller according to the manufacturer. It has large
  puncture-proof tyres and an air-permeable mattress.
  (\href{https://www.bugaboo.com/nl-nl/speciale-aanbiedingen/bugaboo-fox-5-bassinet-and-seat-stroller-black-base-midnight-black-fabrics-midnight-black-sun-canopy-PV006272.html?gad_source=1&gclid=Cj0KCQiA1Km7BhC9ARIsAFZfEIuB-6fQPRl5KyIHVJtion5lyD_Z1Qn-IP3shWoB_HXFozM1ySTXNfgaAgzFEALw_wcB&gclsrc=aw.ds}{Bugaboo
  website})
  \item[Green Machine] An unknown brand vintage perambulator, dating
  approximately from the 1970's that includes a leather strap suspended cot in a
  metal frame. The wheels are relatively large in diameter compared to the
  modern strollers.
  \item[Old Rusty] An unknown brand vintage seat-style stroller from
  approximately the 1970's that includes a metal spring suspension system and
  wheels that are slightly larger than the modern strollers.
\end{description}
\item[Cargo Bicycles] Two modern Dutch ``bakfietsen'' in which different baby
seats can be mounted.
%
\begin{description}
  \item[Urban Arrow Bicycle] A popular electric cargo bicycle in The
  Netherlands. This vehicle has two inline wheels which makes it roll into
  curves like a regular bicycle. It is featured by a long frame that can carry
  loads (e.g. a child in a car seat or baby shell) placed in between the rider
  and the front wheel. 
  (\href{https://urbanarrow.com/}{Urban Arrow website})
  \item[Keiler Tricycle] A tadpole (two wheels in the front, one in the
  rear) cargo tricycle  without electric assist. This vehicle will not roll into
  curves. However, differing road surface unevenness at the left and right front
  wheel will induce lateral roll and lateral acceleration in infants. We added
  masses in specific locations to simulate the presence of an electric motor and
  battery package. (\href{https://kashop.nl/product/keiler-bakfiets/}{Product
  Webpage}) 
\end{description}
\item[Baby Seats] These two baby seats were mounted in the cargo bays of the two
cargo bicycles.
%
\begin{description}
  \item[Maxi-Cosi X Joolz Pebble Pro i-Size Car Seat] Can be adapted to be
  mounted on cargo bicycles with a fitting fixing system (e.g. ``Urban Arrow
  Baby Car Seat Adapter''). Comes with an integrated suspension system. The same
  adapter was used in both cargo bicycles.
    (\href{https://www.maxi-cosi.nl/autostoelen/pebble-pro-i-size}{Maxi-Cosi
    Webpage})
  \item[Melia Baby Shell] Baby seat specifically designed for cargo bicycles
  meant for babies from 2 to 9 months old. Mounted to the seat platform in both
  cargo bicycles.
    (\href{https://melia.nl/product/babyschaal-4-seizoenen-comfort/}{Melia
    Webpage})
\end{description}
\end{description}

>>>>

\color{black}
\begin{abstract}
  Infants transported in strollers and cargo bicycles experience whole-body vibrations. Only little information was found on  these vibrations and the associated comfort and health effects on infants. To improve this, we measure the acceleration of  the seat pan of five strollers and two styles of cargo bicycles with dummy infants representing ages 0 to 9 months over six different road surfaces of varying road roughness, at typical travel speeds. The five strollers included three modern systems and two vintage systems, all with some level of suspension. 
One cargo bicycle had electric support that enabled speeds up to 25~\si{\kph}. We report average seat pan acceleration for 78 different scenarios and investigate the effects of road surface, vehicle, seat type, and travel speed. 
Using the ISO standard for whole-body vibration, we show that rough road surfaces, amplified by travel speed, may have health risks for travel durations as low as \SIrange{10}{30}{\min}. Vintage stroller designs from 50 years ago significantly reduce vibrations compared to  modern strollers tested, indicating the need to return to better suspensions. Cargo bicycles ridden over paver bricks at the maximum speed of an electric bicycle can cause accelerations that should likely be avoided, except for the shortest of durations, until more direct evidence of risks to infants is studied. Vibration standards are needed for infant transport testing and evaluation, designers need to incorporate better suspension for infants, and research is needed to develop clear and direct connections to health and comfort effects.
\end{abstract}

@@

\section{Introduction}
%Paragraph to introduce baby transport
When a baby is born, it is not able to walk and must
be either carried by adults or transported in suitable wheeled
transport. Until about a century ago,  babies mainly stayed at home, which is still customary in some non-Western cultures. A century ago, perambulators were
used to transport infants outdoors. However, mothers were advised that a playpen
in the garden is healthier than the use of perambulators, partly because vibrations generated by a perambulator were deemed not comfortable and even
harmful for babies~\cite{behrend1931}, even though in those days perambulators had ample suspension. Since about 1970, cars became ubiquitous, and the heavy and
sizeable perambulators became strollers: lighter and smaller products foldable for
easy transportation in cars. Over the years, new means of transportation came
into use for infants: child safety seats to use in cars, bicycles with child seats
and cargo bicycles with child seats or baby shells.

%Paragraph to introduce baby vibration in transportation
All means of transport cause vibration, which is transferred to the sitting or lying infant. Unlike the advice in the 1930s, vibration is seemingly
not a subject of attention in the present design of these products. On the contrary, modern strollers do not have much suspension, and (electric) cargo bicycles are increasingly used for infants with seats that offer marginal suspension or padding. We thoroughly reviewed the literature, but found very little about the maximal vibration load that babies and older children can receive during transport without discomfort or harm, and vibrations generated by infant transport are only sparsely investigated.
%Therefore the effect of transport on infant comfort and health can not easily be assessed. 
To establish the amount of vibration to which infants are subjected in
transportation products, we investigated the vibration that infants receive
during transport in strollers and cargo bicycles.

% Paragraph about motivation
Research on vibration comfort during cycling is a logical starting point for investigating similar road-induced vibrations for infants. Cycling is beneficial for
health~\cite{Oja1998} and greatly contributes to reducing CO\(_2\) emissions, congestion, and air pollution~\cite{Neves2019}. As a result, bicycles are
increasingly being used to deliver goods, for daily
commuting and leisure. Among all journeys in the EU, 20-40\% are by
bicycle or on foot, with bicycle trips most frequent in the Netherlands,
Denmark, and Sweden and less frequent in Finland. Various countries and employers provide incentives to increase the use of bicycles. However, the comfort experienced
by riders and passengers (i.e., infants/children in cargo bicycles), is 
a multifaceted ~\cite{ayachi2015identifying} challenge in their wide
acceptance. %Meanwhile, this is a topic that is of great interest and requires attention when it comes to infants' transportation with strollers or bicycles.
% Paragraph about comfort in bicycles
The comfort of bicycles~\cite{too1990biomechanics} is mainly affected by physical
comfort and the impact of environmental factors (weather, route geometry,
and road roughness).  
Physical comfort is related to mechanical (bicycle and component design),
biomechanical (whole-body vibrations, human body dynamics, and kinematics), and
physiological factors (individual characteristics, e.g. sex, body size, weight, etc.).
Although there is relevant literature exploring the impact of environmental
factors (i.e., irregular road surface quality, weather conditions) on cyclist
comfort~\cite{Stinson2003,Hagemeister2003,ayachi2015identifying,Verhoeven2017,Teixeira2020},
there is limited work on understanding the biomechanical and physiological
factors of comfort of bicycle passengers (infants/children in bicycle
seats, cargo bicycles, or trailers). A particular concern is the transport
of infants under one year of age, who cannot well express any experience of discomfort
or pain.
Similar concerns are raised about strollers, where infants are also
exposed to road-induced vibrations. 
In this paper, we will explore biomechanical comfort by assessing whole-body
vibrations experienced by infants transported in cargo
bicycles and strollers, and by evaluating potential health risks and discomfort.

% Paragraph about transmission of vibrations
Biomechanical comfort is mainly related to vibrations induced by road
irregularities and transmitted through the vehicle to the human body ~\cite{too1990biomechanics}. 
Road irregularities are a driving factor, as vibrations induced in children are not efficiently
isolated due to the lack of adequate suspension systems in most bicycle models~\cite{vasudevan2017comparison} and strollers.
The bicycle or stroller design and the seating configuration affect posture and vibration transmission~\cite{Brand2020,Verma2016}.
Children/infants can be
transported sitting or lying in a different location than the cyclist (e.g. above a wheel when in a bicycle seat) and in/on a different `seat'
(a car seat, bicycle seat, stroller seat, or cot). 
%These all influence the transmission of vibrations from the seat to the body and head.
Vibrations increase with travel speed, for example, when
running with a stroller or due to the increased power offered by electric
bicycles (with and without trailers).
For the latter, the average speed using electric bicycles and speed pedelecs is
19\% higher (21.0~\si{\kph} and up to 63\% higher (28.1~\si{\kph}),
respectively, than conventional bicycling~\cite{SWOV2022}.
%The intensity of these vibrations could become even more critical with the change of load, which could be related with age and size of the infant/children transported. 
However, there is limited literature exploring whole-body
vibrations of infants and children transported by bicycle trailers,
cargo bicycles, and strollers 
~\cite{Ota2012,Ota2014,Kanya-Forstner2020, vanDriessche2018,
Schwanitz2020,MalteChildComfort2022}, and literature focusses on comfort rather
than health risks.

% Paragraph about children in bicycles
One of the research fields closely related to the vibrations that act on infants
during transportation is that of inflicted head injury by shaking trauma
(IHI-ST). However, there is a lack of reliable, applicable, and validated injury
thresholds to assess IHI-ST risks~\cite{hutchinson2024modeling}. Similarly,
even if there are indications that vibration affects
comfort in bicycles or strollers, there are no standard vibration assessment methods or
guidelines available with respect to their design. ISO~2631~\cite{ISO2631}, the
international standard for assessing whole-body vibrations, was derived using
data sets on motion platforms, with adults as participants and sitting postures
as adopted in passenger vehicles rather than on bicycles.
Gao~et~al.~\cite{Gao2018} therefore derived vibration
comfort limits for adults riding bicycles, based on their
subjective feedback.
Furthermore, in ISO~2631-1 the exposure time to vibrations is not considered a factor
in the determination of comfort, despite having a clear impact on health risks
according to the European Directive (2002/44/EC, 2002)
\cite{directive2002directive}.

% Paragraph Potential effects of vibrations on adults
Despite the lack of knowledge and test methods with regard to comfort or inflicted head
injury by shaking trauma for children/infants on bicycles, there are clear
indications in the literature that these should be considered.
About 36\% of males and 42\% of females in a total sample of 900 cyclists had
various discomfort complaints~\cite{groenendijk1992sitting}.
Discomfort of both men and women occurred even during short bicycle trips
(\SIrange{3}{10}{\kilo\meter}). However, results from research into comfort of active
adult cyclists cannot be applied directly to infants or children sitting or
lying in transportation systems.

Schwanitz~et~al.~\cite{Schwanitz2020} tested a child bicycle
trailer on smooth asphalt, gravel, and cobblestones using child shaped sandbag dummies (baby and toddler sizes) using ISO~2631-1
weightings. Tyre pressure and number of
passengers had no significant effect on vibration magnitude, but road surface
and travel speed did. 
The baby-sized dummy (5~\si{\kilo\gram}) experienced 20\% higher vibration than
the toddler-sized dummy (10~\si{\kilo\gram}), while the measured values
generally exceeded the ISO~2631-1 limit for vibrational comfort of adults.
Rothhämel~et~al.~\cite{MalteChildComfort2022} tested a
trailer seat and a tadpole configuration three-wheel cargo bicycle on smooth
asphalt and cobblestones for speeds from \SIrange{10}{20}{\kph} using ISO~2631-1 weightings. They found a large
increase in vibration amplitude on cobblestones compared to asphalt in the
same speed range. The child trailer exhibited larger accelerations
than the cargo bicycle with the child seat between the front wheels. 
Child seats in trailers and cargo bicycles generally had
vibrations of higher magnitude than those experienced in a car seat travelling at 30~\si{\kph} on a rough road \cite{gromadowski2013analysis}. Rothhämel and
Liu~\cite{rothhamel2023comfort} conducted measurements with a
6.5~\si{\kilo\gram} mass representing an infant with various tyre pressures. All
their values fell into the ``extremely uncomfortable'' zone for ISO~2631-1.

In addition to studies with dummies or lumped masses representing
infants, Kanya-Forstner~\cite{Kanya-Forstner2020} measured acceleration in
bicycle child trailers with human subjects aged 12 months to 6 years over
asphalt and gravel terrain (average speed of 12~\si{\kph} over a
20~\si{\minute} ride). 
According to the health assessment using ISO~2631-1, the vibrations are similar
to those experienced in child seats in cars and illustrate moderate or low
health risk for a 2~\si{\hour} duration.
On the other hand, if not corrected for duration, the values point to moderate
and high risks. The type of road surface had the greatest influence on the levels of vibration
exposure, followed by type of trailer, while gel cushions as support did not
significantly influence the vibration measured at the seat/pan interface. Hence,
there is a need to refocus on the impact of vibrations on infants and
children's health and comfort~\cite{rybarczyk2020physiological} to ensure 
safe, comfortable and wide use of bicycles.

% Don't edit, working to change the following paragraph
In the context of infants transportation with stroller seats, Kok
Siong~\cite{lim2018study} carried out an indoor and an outdoor experiment to
capture the vibrations at the seat and backrest of a baby
stroller, using weights from \SIrange{4}{14.14}{\kilo\gram}, and  a child
subject of 10.30~\si{\kilo\gram} as well as a dummy weighing
10.30~\si{\kilo\gram}. 
Comfort levels (ISO~2631-1) for indoor testing were  `Fairly
uncomfortable' to `A little uncomfortable', where outdoor testing resulted in
`Extremely uncomfortable' and `Fairly uncomfortable' values. The child and dummy provided similar results. %However, the results still consider ISO~2631-1 standard, which is designed for adults and specific postures. 
Sierzputowski~
et~al.~\cite{sierzputowski2021pilot} tested a modern
and
an older stroller on asphalt road, concrete
paving blocks, concrete plates, dirt road, lawn and damaged concrete. Several conditions resulted in the highest discomfort levels ($>$2~\si{\mps\squared} according to ISO~2631-1). 
Okajima~et~al.~\cite{okajima2020dynamic} tested seven
children, sitting upright in a stroller, riding over a protrusion
(13x60 mm) with either one wheel or two wheels. 
The children were 3 to 6 years old, boys and girls, weighing
\SIrange{15.94}{19.96}{\kilo\gram} with a length of
\SIrange{98.0}{112.4}{\centi\meter}. 
The infant’s head and chest exhibited strong vibrations at
1~\si{\hertz} along all three axes (x, y and z), vibration along the
y-direction at 2~\si{\hertz}, with limited vibration above
8~\si{\hertz}. 
%This result is critical as this range of frequencies is very common in bicycles and strollers. 
However, they did not assess comfort and health risk.

The above studies provide experimental evidence of strong vibrations in real children, dummies, or simple masses transported in cargo bicycles, bike trailers, and strollers.
Most studies use ISO~2631-1 frequency weighting and report very or extremely uncomfortable conditions with higher speeds and rough surfaces, while only one study evaluated health effects. Only a few studies focus on the effect of vibration on babies and infants under 12 months of age.

This paper addresses both comfort and potential health effects for babies and infants.
We equipped five
strollers and two cargo bicycles with inertial measurement units (IMU) and
carried out 78 experiments on different road surfaces and with different travel speeds, using
dummies representing 0, 3, and 9 month-old infants.
We present results using ISO~2631-1
frequency weightings. 
Given that ISO-2631-1 is neither validated for children nor for lying postures, we also report unweighted results to assess power spectrum and bandwidth.
We investigated the influence of vehicle, seat, body size, speed, and road surface
and provide recommendations to users, designers, and future researchers.

\section{Methods}
%
\subsection{Test Equipment}
%
Vibration measurements were conducted at approximately constant speed using five
different strollers and two cargo bicycles with two baby seats, chosen for their
popularity and/or distinctive features. The strollers consisted of three modern
strollers: Maxi-Cosi Street Plus (Dorel Juvenile, Foxborough, USA), BABYZEN YOYO
0+ (Stokke, Ålesund, Norway), Fox 5 (Bugaboo, Amsterdam, The Netherlands) and
two vintage strollers from unknown manufacturers ``Green Machine'' cot-style and
``Old Rusty'' seat-style. The cargo bicycles were a two-wheel UrbanArrow (Pon,
Amsterdam, The Netherlands) and a delta configuration tricycle (Keiler Bakfiets, The Netherlands) which were each fitted with the two seats: Joolz Pebble Pro (Dorel Juvenile, Foxborough, USA), Melia Baby Shell (Melia, Rotterdam, The Netherlands).
~\footnote{Appendix~\ref{app:equipment} provides.
figures and technical descriptions of all strollers and cargo bicycles.}

The tests involved three baby dummies with sizes and weights representative of
newborns and infants 3 and 9 months of age. Newborns (`0 months') are the
youngest (smallest, lightest) children that are transported in strollers with a
cot. Three-month-old infants are the youngest (smallest, lightest) children that
are transported in cargo bicycles, fixed in a baby car seat or baby shell.
Nine month old infants are the youngest (smallest, lightest) that can sit up
straight by themselves and thus can be transported sitting up straight, in a
stroller with a seat or on the bench of a cargo bicycle.

We considered the use of ``crash test dummies'' (also known as anthropomorphic
test devices or ATDs), which are designed and commonly used to test child seats
in car crash tests. However, the closest available body sizes for crash test
dummies do not meet the body sizes desired for this investigation. Furthermore, crash test dummies are of a fundamentally
different design, based on scaling of adult biomechanical data
rather than child data and with dynamic properties designed for crash
conditions, not for vibration testing. Therefore crash test dummies were not considered a good option to use for the envisaged vibration testing.

Testing with real infants would be unethical for the most severe conditions and create challenges in
terms of reproducibility. Hence we bought and adapted ``reborn'' dummies
available in a wide range of postures from a webshop specialising in dolls and
dummies (\href{http://www.atelier-wiesje.nl}{Atelier Wiesje}). The dummies were
filled with a mixture of cat litter, sand, and water to reproduce the exact
weights needed. Cat litter sand features smooth and round shapes
grains, which do not damage the dummies' materials (fabric and plastic). The
weight and body height of the dummies were made to match the average measures
for children of 0, 3 and 9 months old: 3.48~\si{\kg}|50~\si{\cm}
5.90~\si{\kg}|62.5~\si{\cm}, and 8.90~\si{\kg}|70~\si{\cm}, respectively.

%We wanted to use the measurements from Steenbekkers~\cite{Steenbekkers1993}. However, this research provided the results only per three-month group, which did not fit our age categories. 
We used Dutch infant growth charts to determine the average weight and body
height at age 0 months [reference needed!] and French growth charts for 3 and 9
months. French children are the smallest in Europe, and Dutch children are the
tallest. At 3 months, average Dutch children weigh 113 grams more than average
French children and at 9 months, the difference is 85 grams.

To achieve a realistic mass distribution, each limb
was filled with a proper amount of wet sand (for the 0-month dummy, water was
added to achieve the correct weight). To do this, we simplified the geometry of
each body segment according to the defined basic geometric shapes: a sphere for
the head, and cylinders for the torso, upper arms, upper legs and lower legs,
according to~\cite{Snyder1977}. We assumed equal
density for each limb (1000~\si{\kg\per\cubic\meter}), and rescaled the limb segments
in \cite{Snyder1977} to match the dimensions of our dummies. %In doing so, we were able to calculate the volume of each segment, thus the mass of each limb of the dummies.
